Decentralized Data Marketplace to Enable Trusted Machine Economy $^{\dagger}$

### 2019-12-30 paper.tex
Revise the conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

By combining the established standards and openly-developed specifications, this paper proposed an autonomous data marketplace design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.
